\textbf{ \Large {Decentralized autonomous sensor fault detection using neural networks}}

### 2015-02-18 Paper/PaperJahrSchlich.tex
lab ex outline

\section*{Introduction}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics{figures/dataflow_tasks_nn.eps}
    \caption{Dataflow and associated SHM tasks}
    \label{fig:flow}
\end{figure}

@@

\begin{figure}[hbtp]
    \centering
    \includegraphics{figures/neuralnetwork.pdf}
    \caption{Scheme of the neural network}
    \label{fig:neuralnetwork}
\end{figure}

@@

The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the second phase is entered by increasing the sampling rate. 
The measured values are stored in the sensors nodes in an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations to transform the measured values from time domain into frequency domain. 
With the transformed data, the magnitudes and the correlating frequencies of the measured vibrations are calculated.
Finally, the natural frequency is determined by extracting the maximal magnitude.
The \texttt{Measure\-ment} class defines analyzed measurements by storing the following parameters: the address of the sensor node, the maximal magnitude, the natural frequency and a boolean value that indicates if a sensor fault was detected during runtime.
Using the SNIPE library, a neural network is defined and created for fault detection.
The \texttt{Network\-Training} class defines a routine to train the neural network with previously measured \texttt{Measure\-ment} objects.
The \texttt{Communi\-cation} class ensures the wireless communication by opening a radio connection between the sensor node and the basestation to transfer the \texttt{Measure\-ment} objects from the sensor node to the basestation.
For starting the operation of the sensor node, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class, the SNIPE neural network classes, the \texttt{Network\-Training} class and the \texttt{Communi\-cation} class are created to perform the monitoring tasks.

@@

\begin{figure}[htbp]
    \centering
    \includegraphics[width = \textwidth]{figures/uml-basestation.pdf}
    \caption{Class diagram of the \texttt{basestation} package}
    \label{fig:UML-bs}
\end{figure}

@@

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure, as shown in \autoref{fig:teststructure}.
The test structure is a 4-story shear-frame structure consisting of four steel plates of 25\,cm\,$\times$\,50\,cm\,$\times$\,0.8\,mm.
The plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom of the structure, the rods are fixed into a solid block of 40\,cm\,$\times$\,60\,cm\,$\times$\,30\,cm.
The SHM system is installed on the test structure by mounting one wireless sensor node to each of the three top stories.

@@

Ensuring a free vibration in natural frequency with little interferences, the structure is excited by a deflection of the top of the structure.

After excitation, i.e. when the acceleration threshold is exceeded as detected by the sensor nodes, the sensor nodes automatically start measuring the acceleration.
Each sensor node performs a FFT, once sufficient acceleration measurements have been collected.
By applying the FFT, the acceleration measurements are converted into the vibration frequencies and the corresponding magnitudes of the structure \cite{rao2011fast}.

\begin{itemize}
\item \textbf{neuronales Netz}
\item TRAININGSPHASE
\item Austausch der gemessenen FFT zwischen den Sensoren
\item trainieren des neuronalen Netzes, bis keine Verbesserung bei Vorhersagegenauigkeit eintritt
\item MESSPHASE
\item Austausch der gemessenen FFT zwischen den Sensoren
\item Nutzen des neuronalen Netzes, um eventuellen Fehler zu finden
\item KÜNSTLICHEN FEHLER ERZEUGEN
\item TABELLE MIT ERMITTELTEN / GEMESSENEN WERTEN; MIT / OHNE FEHLERN
\end{itemize}

@@

%The implementation of the FFT has been verified by plotting the frequency domain of various vibration events, see \autoref{fig:76hzfft}.
%The natural frequencies can be identified by the peaks in the magnitude graph.
%Each sensor node stores the calculated first natural frequency and the corresponding magnitude in a \texttt{Measurement} object and transmits the object to the other sensor nodes.

>>>>

%----------------------------------------------------------------------------------------
\section*{Introduction}

@@

\begin{figure}[hbt]
    \centering
    \includegraphics{figures/dataflow_tasks_nn.eps}
    \caption{Dataflow and associated SHM tasks}
    \label{fig:flow}
\end{figure}

@@

\begin{figure}[hbt]
    \centering
    \includegraphics{figures/neuralnetwork.pdf}
    \caption{Scheme of the neural network}
    \label{fig:neuralnetwork}
\end{figure}

@@

The \texttt{Acceleration\-Sampler} class is responsible for measuring the acceleration.
There are two phases: first, the acceleration is measured with a low sampling rate.
Once the acceleration exceeds a threshold, the second phase is entered by increasing the sampling rate. 
The measured values are stored in the sensors nodes in an array.
The different phases are indicatad by lighting different LEDs.
The \texttt{FFT} class performs a FFT on the measured accelerations to transform the measured values from time domain into frequency domain. 
With the transformed data, the magnitudes and the correlating frequencies of the measured vibrations are calculated.
Finally, the natural frequency is determined by extracting the maximal magnitude.
The \texttt{Measure\-ment} class defines analyzed measurements by storing the following parameters: the address of the sensor node, the maximal magnitude, the natural frequency and a boolean value that indicates if a sensor fault was detected during runtime.
Using the SNIPE library, a neural network is described and created for fault detection.
The \texttt{Network\-Training} class defines a routine to train the neural network with previously measured \texttt{Measure\-ment} objects.
The \texttt{Communi\-cation} class ensures the wireless communication by opening a radio connection between the sensor node and the basestation to transfer the \texttt{Measure\-ment} objects from the sensor node to the basestation.
For starting the operation of the sensor node, the entry point of the programm is the \texttt{start\-App()} method in the \texttt{Main\-Spot} class. 
Within the \texttt{Main\-Spot} class, instances of the \texttt{Acceleration\-Sampler} class, the \texttt{FFT} class, the SNIPE neural network classes, the \texttt{Network\-Training} class and the \texttt{Communi\-cation} class are created to perform the monitoring tasks.

@@

%\begin{figure}[htbp]
%    \centering
%    \includegraphics[width = \textwidth]{figures/uml-basestation.pdf}
%    \caption{Class diagram of the \texttt{basestation} package}
%    \label{fig:UML-bs}
%\end{figure}

@@

To validate the proposed approach in laboratory experiments, the wireless SHM system is installed on a test structure, as shown in \autoref{fig:teststructure}.
The test structure is a 4-story shear-frame structure consisting of four steel plates of 25\,cm\,$\times$\,50\,cm\,$\times$\,0.8\,mm.
The plates are mounted on threaded rods with a vertical clearance of 23\,cm.
At the bottom of the structure, the rods are fixed into a solid block of 40\,cm\,$\times$\,60\,cm\,$\times$\,30\,cm.
The SHM system is installed on the test structure by mounting one wireless sensor node to each of the three top stories.
Ensuring a free vibration in natural frequency with little interferences, the structure is excited by a deflection of the top of the structure.

@@

Several test runs were conducted.
During each test run, all sensor nodes run simultaneously.
A test run includes a training phase and a data collection phase.
The training phase consists of the description, the creation and the training of a neural network.
During the training of the neural network, several measurements are performed and used as training input.
A measurement includes the excitation of the structure, acceleration sampling, calculation of the natural frequency and corresponding magnitude, and data exchange with the other sensor nodes.

The data collection phase consists of any desired number of measurements, sensor fault detection, and data storage.
After every measurement, the measured magnitudes of the other sensor nodes are used as input of the neural network to predict the expected magnitude of the embedding sensor nodes for sensor fault detection.
The deviation of the expected magnitude and the measured magnitude is calculated.
If the deviation exceeds a threshold, a sensor fault is assumed.
After the sensor fault detection, the following are stored into the database: the time of the measurement, the natural frequency, the measured magnitude, the expected magnitude, the deviation,  and a boolean value that indicates if a sensor fault was detected.

In several test runs, the properties of the neural network are optimized.

has been tested with varying numbers of training measurements (\autoref{fig:traininputs}).
With increasing numbers of training measurement, the prediction accuracy increases.

The neural network has been validated by repeated tests---using varying excitation forces, varying sampling rates, and varying quantities of measured values.

The implementation of the FFT has been verified by plotting the frequency sprectrum of various vibration measurements, (\autoref{fig:76hzfft}).
The natural frequencies can be identified by the peaks in the magnitude graph.
Each sensor node stores the calculated first natural frequency and the corresponding magnitude in a \texttt{Measurement} object and transmits the object to the other sensor nodes.

\begin{itemize}
\item \textbf{neuronales Netz}
%\item TRAININGSPHASE
%\item Austausch der gemessenen FFT zwischen den Sensoren
%\item trainieren des neuronalen Netzes, bis keine Verbesserung bei Vorhersagegenauigkeit eintritt
%\item MESSPHASE
%\item Austausch der gemessenen FFT zwischen den Sensoren
%\item Nutzen des neuronalen Netzes, um eventuellen Fehler zu finden
\item KÜNSTLICHEN FEHLER ERZEUGEN
\item TABELLE MIT ERMITTELTEN / GEMESSENEN WERTEN; MIT / OHNE FEHLERN
\end{itemize}

@@

%After excitation, i.e. when the acceleration threshold is exceeded as detected by the sensor nodes, the sensor nodes automatically start measuring the acceleration.
%Each sensor node performs a FFT, once sufficient acceleration measurements have been collected.
%By applying the FFT, the acceleration measurements are converted into the vibration frequencies and the corresponding magnitudes of the structure \cite{rao2011fast}.
